Linear and Differential Cryptanalysis of DES

### 2009-01-30 trunk/talk/draft1.tex
Fixed r21 break

\subsection{Independence of S-Boxes}
\begin{frame}
Refresh math idea ... Independence assumption ...

>>>>

\subsection{Independence of S-Boxes}
\begin{frame}
Note that throughout this discussion we have assumed that the S-Boxes were independant. This allowed us to use the Piling Up Principle to combine linear approximations of S-Boxes across rounds. \\
\vspace{3mm}
This assumption worked well for us in practice, but is not necessarily true. We could have proceeded differently without this assumption - [see John Manferdelli's Boolean Functions slides]
\end{frame}
